PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-27 paper/paper.tex
added bib file, starting melody section

@@

\begin{thebibliography}{citations}

\bibitem {Author:00}
E. Author:
``The Title of the Conference Paper,''
{\it Proceedings of the International Symposium
on Music Information Retrieval}, pp.~000--111, 2000.

\bibitem{Someone:10}
A. Someone, B. Someone, and C. Someone:
``The Title of the Journal Paper,''
{\it Journal of New Music Research},
Vol.~A, No.~B, pp.~111--222, 2010.

\bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
    Editorial Acme, Porto, 2012.

\end{thebibliography}

%\bibliography{ismir2014template}

>>>>

\subsection{Melody Extraction}
Melody extraction, or predominant fundamental frequency ($f_0$) estimation,
involves the estimation of the pitch ($f_0$) sequence of the melody from a
polyphonic music recording \cite{salamon:MelodyReview:IEEESPM13}.

@@

% \begin{thebibliography}{citations}
% 
% \bibitem {Author:00}
% E. Author:
% ``The Title of the Conference Paper,''
% {\it Proceedings of the International Symposium
% on Music Information Retrieval}, pp.~000--111, 2000.
% 
% \bibitem{Someone:10}
% A. Someone, B. Someone, and C. Someone:
% ``The Title of the Journal Paper,''
% {\it Journal of New Music Research},
% Vol.~A, No.~B, pp.~111--222, 2010.
% 
% \bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
%     Editorial Acme, Porto, 2012.
% 
% \end{thebibliography}

\bibliography{mir_eval}
